Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-25 8-Discussion.tex
update

\todo[inline]{on pourrait aussi répondre ici aux 3 questions posées
explicitement (copiées dansl'intro pour le moment), a priori non, le chef
trouve que c'est chiant}

@@

Our solution is fully tooled by a ``free'' ad hoc tool. We use the Openflexo
infrastructure to design models and metamodels together. In addition, our
infrastructure also produces a dedicated tool which allows processes execution.
In our approach,

\subsection{model verification}

@@

>>>>

\todo[inline]{on pourrait aussi répondre ici aux 3 questions posées
explicitement (copiées dans l'intro pour le moment), a priori non, le chef
« trouve que c'est chiant »}

@@

Our solution is fully tooled by a ``free'' ad hoc tool. We use the Openflexo
infrastructure to build models and metamodels together. In addition to the
solution, it also provides a dedicated tool which allows processes execution. 
\noteJC{dire qqch sur le fait que produire une solution avec son outil associé
  est une force, genre ``Providing a solution and its associated tool can be
…'' mais pour le moment je ne vois pas comment l'enchainer}

\subsection{Model verification}

@@

By default, our tooling does not include a lot of automated verifications.
However, a user can add verification mechanisms by writing new behaviors
attached to concepts. Presently, the verifications rely on the users when they
build the metamodels and the models.
